### 2022-01-13 manuscript/manuscript.Rmd
Update manuscript.Rmd

abstract: |
  Critical scrutiny of published scientific research, often called post-publication peer review (PPPR), can highlight errors, limitations, or alternative interpretations that were not adequately addressed during traditional peer review. Currently, there is limited empirical data documenting how academic journals handle this important aspect of scientific self-correction. We assessed PPPR policies and practice amongst 330 influential journals operating across 22 scientific disciplines. 123 (37%) journals did not offer any options for submitting PPPR. 207 (63%) journals offered PPPR options such as letters, commentaries, or web comments, but often imposed limits on length (median 1000, IQR 700 words) and time-to-submit (median 12, IQR 22 weeks). The most restrictive limits were 175 words and 2 weeks. Of a random sample of 2066 research articles published in 2018 by PPPR-offering journals, we found that 1.9% (95% CI [1.4, 2.6]) were the subject of at least one PPPR. Examination of 58 PPPRs found, for example, that 44 received an author reply, of which 41 asserted that the authors’ conclusions were unchanged. Clinical Medicine stood out as the domain with the most active PPPR culture, with all 15 journals providing PPPR options and publishing the most PPPR, but also imposing the strictest length limits (median 400, IQR 150 words) and time-to-submit limits (median 4, IQR 2 weeks). Overall, our findings suggest that influential academic journals often pose serious barriers to the cultivation, documentation, and dissemination of PPPR. We propose several policy changes that journals could adopt to promote a richer culture of post-publication critique.

>>>>

abstract: |
  Critical scrutiny of published research is an important feature of a self-correcting scientific ecosystem. Academic journals exert considerable control over criticism submitted in the form of letters, commentaries, or online comments (post-publication peer review, PPPR). Currently, there is only limited empirical data documenting how journals handle PPPR. We assessed PPPR policies and practice amongst 330 influential journals operating across 22 scientific disciplines. 123 (37%) journals did not offer any options for submitting PPPR. 207 (63%) journals offered PPPR options, but often imposed limits on length (median 1000, IQR 700 words) and time-to-submit (median 12, IQR 22 weeks). The most restrictive limits were 175 words and 2 weeks. Of a random sample of 2066 research articles published in 2018 by PPPR-offering journals, we found that 1.9% (95% CI [1.4, 2.6]) were the subject of at least one PPPR. Examination of 58 PPPRs found, for example, that 44 received an author reply, of which 41 asserted that the authors’ conclusions were unchanged. Clinical Medicine stood out as the domain with the most active PPPR culture, with all 15 journals providing PPPR options and publishing the most PPPR, but also imposing the strictest length limits (median 400, IQR 150 words) and time-to-submit limits (median 4, IQR 2 weeks). Overall, our findings suggest that influential academic journals often pose serious barriers to the cultivation, documentation, and dissemination of PPPR. We propose several policy changes that journals could adopt to promote a richer culture of post-publication critique.
